Uncovering Distributed System Bugs\\ during Testing (not Production!)

### 2015-08-18 intro.tex
updates in overview

Classic techniques that product groups employ to test, verify and validate their systems (such as code reviews, stress testing and fault injection) are unable to capture and control all the aforementioned sources of nondeterminism, which causes the most tricky bugs being missed during testing and only getting exposed after a system has been put in production. Discovering and fixing bugs in production, though, is bad for business as it can cost a lot of money and many dissatisfied customers.

>>>>

Classic techniques that product groups employ to test, verify and validate their systems (such as code reviews, unit testing, stress testing and fault injection) are unable to capture and control all the aforementioned sources of nondeterminism, which causes the most tricky bugs being missed during testing and only getting exposed after a system has been put in production. Discovering and fixing bugs in production, though, is bad for business as it can cost a lot of money and many dissatisfied customers.

### 2015-08-18 overview.tex
updates in overview

All these sources of nondeterminism (as well as nondeterminism due to timeouts, message losses and client requests) can easily create \emph{heisenbugs}~\cite{musuvathi2008finding}, which are corner-case bugs that are difficult to detect, diagnose and fix, without using advanced \emph{asynchrony-aware} testing techniques.
%
The ideal testing tool should be able to work on unmodified systems, capture and control all possible sources of nondeterminism, systematically inject faults in the right places, and explore all feasible execution paths. However, this is easier said than done when testing production systems.

There are two types of bugs that developers of distributed systems are mostly interested in finding: \emph{safety} and \emph{liveness} property violations~\cite{lamport1977proving}.

@@

Although a significant amount of research has been conducting during the past few decades on how to test distributed systems,

only a small amount of this research was successful enough to be picked up by industry.

>>>>

All these sources of nondeterminism (as well as nondeterminism due to timeouts, message losses and client requests) can easily create \emph{heisenbugs}~\cite{gray1986computers, musuvathi2008finding}, which are corner-case bugs that are difficult to detect, diagnose and fix. The majority of bugs in distributed systems can be classified in two categories: \emph{safety} and \emph{liveness} property violations~\cite{lamport1977proving}.

@@

A significant amount of research has been conducted during the past few decades on how to test distributed systems~\cite{lamport1977proving, lamport1994temporal, schuppan2004efficient, killian2007life, gupta2008diecast, yang2009modist}, but it is still not clear how to successfully apply all these research techniques in a real production environment, which can be full of complications~\cite{cavage2013there, maddox2015test}.

Product groups today rely on techniques such as unit testing, integration testing and stress testing, which although can catch many bugs, are unable to catch the most tricky ones, which can be caught only by using advanced \emph{asynchrony-aware} testing techniques. The ideal testing tool should be able to work on unmodified distributed systems, capture and control all possible sources of nondeterminism, systematically inject faults in the right places, and explore all feasible execution paths. However, this is easier said than done when testing production systems.
